The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-01-21 src/ms.tex
Add citations for coordinated packages

Several of the affiliated packages described in [reference to paper 2] 
have had substantial improvements. \texttt{Astroquery} [reference] has added access 
to roughly a dozen new missions and data services, including JWST, and the 
project has switched to a continuous release model. Every time a change 
is committed to the main development branch it is published on the Python 
Package Index (PyPI, ref) and available for installation. Formal releases 
are still done a couple of times per year. \texttt{Photutils} released its first 
stable version, indicating that the API will change less frequently, and 
there have been several significant performance improvements.  \texttt{CCDproc} 
also released a new major version, bringing better performance to some 
image combination operations. The \texttt{regions} package, for manipulating 
ds9-style [ref] region definitions, added new ways to manipulate regions 
and introduced new region types. \texttt{Reproject}’s major new feature is a 
function to align and co-add images to create a mosaic; better support 
for parallelization was also added. \texttt{Specutils}, the package that defines 
containers for 1D and 2D spectra, also had its first stable rele and 
the addition of classes to read JWST data.

>>>>

Several of the affiliated packages described in [reference to paper 2] have
had substantial improvements. \texttt{astroquery} \cite{astroquery} has added
access to roughly a dozen new missions and data services, including JWST, and
the project has switched to a continuous release model. Every time a change
is committed to the main development branch it is published on the Python
Package Index (PyPI, ref) and available for installation. Formal releases are
still done a couple of times per year. \texttt{photutils} \cite
{photutils} released its first stable version, indicating that the API will
change less frequently, and there have been several significant performance
improvements.  \texttt{ccdproc} \cite{ccdproc} also released a new major
version, bringing better performance to some image combination operations.
The \texttt{regions} package \cite{pyregions}, for manipulating ds9-style
region definitions \cite{ds9}, added new ways to manipulate regions and
introduced new region types. \texttt{reproject}’s \cite{reproject} major new
feature is a function to align and co-add images to create a mosaic; better
support for parallelization was also added. \texttt{specutils}, the package
that defines containers for 1D and 2D spectra \cite{specutils}, also had its
first stable release and the addition of classes to read JWST data.
